---
title: "MATH1324 Assignment 1"
subtitle: Modeling Body Measurements
output:
  html_notebook: default
  html_document:
    df_print: paged
---

## Student Details

Prashant kumar (S3790132)

## Problem Statement
* We have a data of body measurement for both sexes.We are going to select bisceps girth data for both the sexes for analization.We are going to see that in general which of the sexes tends to have more bisceps girth 

## Load Packages

```{r}
# This is a chunk where you can load the necessary packages required to reproduce the report
library(dplyr)
library(rvest)
library(readr)
library(foreign)
library(knitr)

```

## Data
* bdims.csv data was imported into Rstudio using read_csv function.
* I have selected the bic.gi variable for assesment in both male and female sex.
* I have used the matrix function to create two seperate table namely "male"
  and "female" which has 2 variable each "bic.gir" and "sex".

```{r}
bdims_csv_bdims_csv <- read_csv("E:/RMIT SEMESTER1/INTRO TO STATS/bdims.csv - bdims.csv.csv")
#chossing only bic.gi variable for further analysis.
bodydim<-subset(bdims_csv_bdims_csv[ ,c(16,25)])
#factoring sex variable
sex<-factor(c("1","0"),levels = c("1","0"),ordered = TRUE)
#creating seperate tables for male and female.
male<-bodydim[0:247, ]
female<-bodydim[248:507, ]
```

## Summary Statistics
Mean,Median,IQR,1st quartile,3rd quartile and variance for both the sex is shown in this section.
```{r}
 #summary statistics for male bisceps girth.
summary(male$bic.gi)
IQR(male$bic.gi)
var(male$bic.gi)
sd(male$bic.gi)
#summary statistics for female bisceps girth.
summary(female$bic.gi)
IQR(female$bic.gi)
var(female$bic.gi)
sd(female$bic.gi)

```

## Distribution Fitting

```{r}
#analysing male bic.gir histogram with normal distribution.
malebic<-male$bic.gi
mu1<-mean(malebic)
sd1<-sqrt(var(malebic))
hist(malebic,col="blue",breaks = 21,prob=TRUE,xlim = c(25,45),main = "Histogram plot of male bisceps girth")
curve(dnorm(x,mean = mu1,sd=sd1),col="black",lwd=2,add=TRUE,yaxt="n")
#making emperical distribution cumulative function bic.gi in males.
mbic.gi.ecdf<-ecdf(male$bic.gi)
mbic.gi.ecdf
plot(mbic.gi.ecdf,main="Emperical cumulative function distribution of Male bisceps data")
curve(dnorm(x, mean=mu1, sd=sd1), col="green", lwd=2, add=TRUE, yaxt="n")
#analysing female bic.gir histogram with normal distribution.
femalebic<-female$bic.gi
mu0<-mean(femalebic)
sd0<-sqrt(var(femalebic))
hist(femalebic,col="red",breaks = 21,prob=TRUE,xlim = c(25,45),main = "Histogram plot of female bisceps girth")
curve(dnorm(x,mean = mu0,sd=sd0),col="black",lwd=2,add=TRUE,yaxt="n")
#making emperical cumulative function distribution for bic.gi in females.
fbic.gi.ecdf<-ecdf(female$bic.gi)
fbic.gi.ecdf
plot(fbic.gi.ecdf,main="Emperical cumulative function distribution of female bisceps data")
curve(dnorm(x, mean=mu0, sd=sd0), col="green", lwd=2, add=TRUE, yaxt="n")

```

## Interpretation

* On plotting the distribution curve for bisceps girth in both sexes we can see that most of the males have bisceps girth higher than females.Most males tends to have a bicseps girth in between 33-37 as compared to 26-29 in females.
* Compared to female histogram,male histogram are more normally distributed as generally males have higher bisceps girth than females.Similarly female histogram distributions are more positive/right skewed as generally females have lower bisceps girth than males. 
* On analizing the emperical distribution curve we can see that most of the female bisceps data lies below 30 while for most men it is above 30.
* Thus most men tends to have higher bisceps girth than females.

